Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses

### 2022-09-27 RR_manuscript/Draft_RR.Rmd
remove crossref for section

We calculated summary statistics describing variation among analyses, including (a) the nature and number of acoustic measures (e.g. f0 or duration), (b) the operationalization and the temporal domain of measurement (e.g. mean of an interval or value at specified point in time), (c) the nature and number of model parameters for both fixed and random effects (if applicable), (d) the nature and reasoning behind inferential assessments (e.g. dichotomous decision based on *p*-values, ordinal decision based on a Bayes factor), as well as the (e) mean, (f) standard deviation and (g) range of the standardized effect sizes (see the next section for the standardization procedure).
These summary statistics are reported in \@ref{descr-stats} of the Results section.

@@

We investigated the variability in \textsc{reported effect sizes} using Bayesian meta-analytic techniques.
As the measure of variability, we took the meta-analytic \textsc{group-level standard deviation} ($\sigma_{\alpha_{\text{t}}}$, see below), where the groups are the analysis teams.
As we detail in Section \@ref{meta-est}, we have also run further non-preregistered analyses.
For these we refer the reader to that section, while we only describe the preregistered analyses in the following paragraphs.

>>>>

We calculated summary statistics describing variation among analyses, including (a) the nature and number of acoustic measures (e.g. f0 or duration), (b) the operationalization and the temporal domain of measurement (e.g. mean of an interval or value at specified point in time), (c) the nature and number of model parameters for both fixed and random effects (if applicable), (d) the nature and reasoning behind inferential assessments (e.g. dichotomous decision based on *p*-values, ordinal decision based on a Bayes factor), as well as the (e) mean, (f) standard deviation and (g) range of the standardized effect sizes (see the next section for the standardization procedure).
These summary statistics are reported in *Descriptive statistics* of the Results section.
<!-- Add crossref to final version: \@ref(descr-stats) -->

@@

We investigated the variability in \textsc{reported effect sizes} using Bayesian meta-analytic techniques.
As the measure of variability, we took the meta-analytic \textsc{group-level standard deviation} ($\sigma_{\alpha_{\text{t}}}$, see below), where the groups are the analysis teams.
As we detail in Section *Meta-analytic estimation*, we have also run further non-preregistered analyses. <!-- Add crossref to final version: \@ref(meta-est) -->
For these we refer the reader to that section, while we only describe the preregistered analyses in the following paragraphs.

### 2022-09-27 RR_manuscript/Draft_RR.tex
remove crossref for section

We calculated summary statistics describing variation among analyses, including (a) the nature and number of acoustic measures (e.g.~f0 or duration), (b) the operationalization and the temporal domain of measurement (e.g.~mean of an interval or value at specified point in time), (c) the nature and number of model parameters for both fixed and random effects (if applicable), (d) the nature and reasoning behind inferential assessments (e.g.~dichotomous decision based on \emph{p}-values, ordinal decision based on a Bayes factor), as well as the (e) mean, (f) standard deviation and (g) range of the standardized effect sizes (see the next section for the standardization procedure).
These summary statistics are reported in @ref\{descr-stats\} of the Results section.

@@

We investigated the variability in \textsc{reported effect sizes} using Bayesian meta-analytic techniques.
As the measure of variability, we took the meta-analytic \textsc{group-level standard deviation} (\(\sigma_{\alpha_{\text{t}}}\), see below), where the groups are the analysis teams.
As we detail in Section @ref\{meta-est\}, we have also run further non-preregistered analyses.
For these we refer the reader to that section, while we only describe the preregistered analyses in the following paragraphs.

>>>>

We calculated summary statistics describing variation among analyses, including (a) the nature and number of acoustic measures (e.g.~f0 or duration), (b) the operationalization and the temporal domain of measurement (e.g.~mean of an interval or value at specified point in time), (c) the nature and number of model parameters for both fixed and random effects (if applicable), (d) the nature and reasoning behind inferential assessments (e.g.~dichotomous decision based on \emph{p}-values, ordinal decision based on a Bayes factor), as well as the (e) mean, (f) standard deviation and (g) range of the standardized effect sizes (see the next section for the standardization procedure).
These summary statistics are reported in \emph{Descriptive statistics} of the Results section.

@@

We investigated the variability in \textsc{reported effect sizes} using Bayesian meta-analytic techniques.
As the measure of variability, we took the meta-analytic \textsc{group-level standard deviation} (\(\sigma_{\alpha_{\text{t}}}\), see below), where the groups are the analysis teams.
As we detail in Section \emph{Meta-analytic estimation}, we have also run further non-preregistered analyses.
For these we refer the reader to that section, while we only describe the preregistered analyses in the following paragraphs.
